---
title: "Day 1 Homework"
output: html_document
---

# Before you start working on this homework, complete the primer **The Basics**

In the left sidebar, click Primers (you can hold Ctrl or Cmd when you click Primers to open it in a new window). Please complete both `Visualization Basics` and `Programming Basics`.

# Homework starts below

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

In the code chunk below:

- Create and object named `day` (don't put those ticks in the object naem), and put `1:31` in that object.

- Use `str()` function on object `day` to learn about what type of object it is.

- Use the functions `class()` and `typeof()` on your the object `day`

```{r}

```

## Question 2

- Calculate length of vector `day` and assign it to object `len`

- create a new object called `month` that contains the word "July" repeated `len` times. You can use the function `rep()` to create the object `month`

- Also, create an object `year` that contains `2020` repeated `len` times.

```{r}

```

## Question 3

Now create a dataframe object called `next_month` that will have three columns: year, month, and day. The columns year, month, and day will contain values from the object created in previous questions, respectively. You can use the function `data.frame()` to creat the dataframe. Feel free to look up online on how to use the `data.frame()` function.

```{r}

```

## Question 4

- Navigate to `data-formatting` folder, and open `data-formatting.Rmd` and read it.

- Once you finish reading, click `Knit` and see what happens.









